Detection of Oscillations in Aldebaran with Ground-Based Observations

### 2017-09-21 paper/aldebaran.tex
habitability stub
habitability

>>>>

We note that with the determination of the stellar mass it is possible to infer the parameters Aldebaran had while it was on the main sequence. We conduct a Monte Carlo simulation, drawing masses randomly from a Gaussian distribution $M \sim \mathscr{N}(1.17,0.05)$ to predict the luminosity of the main-sequence progenitor, and the semi-major axis of the planet's orbit, using the scaling relations of \citep{eker2015}, finding that it would have had a luminosity $L_* = 2.0 \pm 0.37~\lsun$ on the main sequence.

We note that this implies that the planet at a semimajor axis of $1.512 \pm 0.021$~AU would have been subject to an insolation of $0.87 \pm 0.14$ times that of the Earth. Subject as well as this to the great uncertainties of the planet's orbital evolution and albedo, this planet and any of its moons may well have had temperate environments now long-since destroyed by their host star's evolution away from the main sequence.
